---
title: 'Homework #9'
author: "Isaac Schennum (no team members)"
repo: "https://github.com/Isaac-Schennum/DS202HW9"
date: "4/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1:

```{r}
library(tidyverse)
av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)
head(av, 35)
```

```{r}
deaths <- av
deaths <- deaths %>% mutate(Time = 1)
deaths <- deaths %>% mutate(Death = "no")
deaths <- deaths %>% mutate(Time = ifelse(Death2 == "", Time, 2))
deaths <- deaths %>% mutate(Time = ifelse(Death3 == "", Time, 3))
deaths <- deaths %>% mutate(Time = ifelse(Death4 == "", Time, 4))
deaths <- deaths %>% mutate(Time = ifelse(Death5 == "", Time, 5))
deaths <- deaths %>% mutate(Death = ifelse(Time == 1 & Death1 == "YES", "yes", Death))
deaths <- deaths %>% mutate(Death = ifelse(Time == 2 & Death2 == "YES", "yes", Death))
deaths <- deaths %>% mutate(Death = ifelse(Time == 3 & Death3 == "YES", "yes", Death))
deaths <- deaths %>% mutate(Death = ifelse(Time == 4 & Death4 == "YES", "yes", Death))
deaths <- deaths %>% mutate(Death = ifelse(Time == 5 & Death5 == "YES", "yes", Death))
deaths <- subset(deaths, select = -c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21))
```

```{r}
returns <- av
returns <- returns %>% mutate(Time = 0)
returns <- returns %>% mutate(Return = "yes")
returns <- returns %>% mutate(Time = ifelse(Return1 == "", Time, 1))
returns <- returns %>% mutate(Time = ifelse(Return2 == "", Time, 2))
returns <- returns %>% mutate(Time = ifelse(Return3 == "", Time, 3))
returns <- returns %>% mutate(Time = ifelse(Return4 == "", Time, 4))
returns <- returns %>% mutate(Time = ifelse(Return5 == "", Time, 5))
returns <- returns %>% mutate(Return = ifelse(Time == 0, "never died", Return))
returns <- returns %>% mutate(Return = ifelse(Time == 1 & Return1 == "NO", "no", Return))
returns <- returns %>% mutate(Return = ifelse(Time == 2 & Return2 == "NO", "no", Return))
returns <- returns %>% mutate(Return = ifelse(Time == 3 & Return3 == "NO", "no", Return))
returns <- returns %>% mutate(Return = ifelse(Time == 4 & Return4 == "NO", "no", Return))
returns <- returns %>% mutate(Return = ifelse(Time == 5 & Return5 == "NO", "no", Return))
returns <- subset(returns, select = -c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21))
```

```{r}
head(deaths, 35)
```

Time: Time character was last seen (counted in appearances - each death marks a new appearance; 1 through 5)

Death: Did the character die the last time they were seen? (yes/no)

```{r}
head(returns, 35)
```

Time: Time character last returned/didn't return (counted in deaths; 0 through 5)

Return: Did the character return the last time they died? (yes/no/never died)

## Part 2:

Claim being fact-checked: Out of 173 listed Avengers, my analysis found that 69 had died at least one time after they joined the team.

```{r}
diedAtLeastOneTime <- returns %>% filter(Return != "never died")
summary(diedAtLeastOneTime)
```

Length = 69 (69 Avengers died at least one time)

The claim passed the fact check.
